\section{Conclusion}
We implement the iterative SVM algorithm based on Hadoop with the plug-in Harp. The above result has given us sufficient proof of preference using Harp to implementing SVM algorithms over other method. By using Hadoop, we fully benefit from the characteristics of distributed computing. As for multiple iterations, Harp gives us inspiration of how to communicate among the nodes with least operations. If not the best, it is a great way to balance between getting the least of necessary communication and the most of important information.

Aside of runtime, we are also concerned about the efficiency. Our result has shown the Harp implementation uses less execution time than simply Hadoop, while not sacrificing the accuracy. From the result of our implementation, we can see that support vector machine models have better performance on Hadoop by adding on the plugin Harp. The performance is optimized by 80\% of MNIST-Harp compared to MNIST-Hadoop. Hadoop generate read and write operations at each iteration while Harp stores support vectors in cache so the runtime is largely reduced. Finally, for each model we can find a global support vector set which is stable and therefore represent the output result. This is easy to understand, since Harp targets to improve the communication process in distributed computing. Moreover, we can therefore apply the presumption that Harp works better on iterative distributed computing to all related algorithms. Experiments need to be done in order to give absolute proof, though. However, for other non-iterative algorithms, we may still prefer Hadoop for its simplicity.
